CloneOverflow: \\ Discovery of Online Code Clones between \\Stackoverflow and Open Source Projects

### 2016-10-20 latex-acm/cloneoverflow.tex
Updated stale clones

The manual investigation of 48 class-A online clone pairs reveals that there are 27 stale clones. They are clone pairs that were copied from Qualitas projects to Stackoverflow and marked as \textit{accepted} answers.  The investigation results are described in Table \ref{tab:stale_code}.

\begin{table}[H]
	\centering
	\caption{Investigation of sale code clones from the online clone pairs}
	\label{tab:stale_code}
	\begin{tabular}{l|r|r|r}
		\hline 
		Project & Pairs & Stale & Fresh \\
		\hline
		apache-ant & 1 & 0 & 1 \\
		aspectj & 2 & 2 & 0 \\
		hadoop & 14 & 9 & 5 \\
		hibernate & 16 & 2 & 14 \\
		jasperreports & 2 & 2 & 0 \\
		jfreechart & 4 & 4 & 0 \\
		jgraph & 5 & 5 & 0 \\
		jgrapht & 1 & 0 & 1 \\
		junit & 3 & 3 & 0 \\
		\hline
		Total & 48 & 27 & 21 \\
		\hline
	\end{tabular} 
\end{table}

>>>>

The manual investigation of 48 class-A online clone pairs reveals that there are 30 stale clones. They are clone pairs that were copied from Qualitas projects to Stackoverflow and marked as \textit{accepted} answers.  The investigation results are described in Table \ref{tab:stale_code}.

\begin{table}[H]
	\centering
	\caption{Investigation of stale code clones from the online clone pairs}
	\label{tab:stale_code}
	\begin{tabular}{l|r|r|r}
		\hline 
		Project & Pairs & Stale & Fresh \\
		\hline
		apache-ant & 1 & 0 & 1 \\
		aspectj & 2 & 2 & 0 \\
		hadoop & 14 & 9 & 5 \\
		hibernate & 16 & 5 & 11 \\
		jasperreports & 2 & 2 & 0 \\
		jfreechart & 4 & 4 & 0 \\
		jgraph & 5 & 5 & 0 \\
		jgrapht & 1 & 0 & 1 \\
		junit & 3 & 3 & 0 \\
		\hline
		Total & 48 & 30 & 18 \\
		\hline
	\end{tabular} 
\end{table}

\begin{table*}
	\centering
	\caption{30 stale code clones found by a manual investigation}
	\label{tab:stale_code_details}
	\begin{tabular}{r|l|r|r}
		\hline 
		No. & File & Stackoverflow Q\&A & Change date \\
		\hline
		1 & aspectjtools1.6.9-src/../Agent.java & 18303692 & 2015-09-08 \\
		2 & aspectjweaver1.6.9-src/../Agent.java & 18303692 & 2015-09-08 \\
		3 & hadoop-1.0.0/../WritableComparator.java & 22315734 & 2014-11-20 \\
		4 & hadoop-1.0.0/../StringUtils.java & 801987 & 2013-02-04 \\
		5 & hadoop-1.0.0/../DBCountPageView.java & 21702608 & 2011-06-12 \\
		6 & hadoop-1.0.0/../DBCountPageView.java & 21702608 & 2011-06-12 \\
		7 & hadoop-1.0.0/../LineRecordReader.java & 16180910 & 2011-07-25 \\
		8 & hadoop-1.0.0/../LineRecordReader.java & 16180910 & 2011-07-25 \\
		9 & hadoop-1.0.0/../JobSubmissionFiles.java & 14845581 & 2012-06-25 \\
		10 & hadoop-1.0.0/../TextOutputFormat.java & 16928749 & 2011-06-12 \\
		11 & hadoop-1.0.0/../TestJobCounters.java & 18833798 & 2011-06-12 \\
		12 & hibernate-release-4.2.2.Final/../SettingsFactory.java & 8257554 & 2011-03-11 (deleted) \\
		13 & hibernate-release-4.2.2.Final/../Example.java & 24924255 & 2013-04-23 \\
		14 & hibernate-release-4.2.2.Final/../SQLServer2005LimitHandler.java.java & 23967852 & 2013-04-23 \\
		15 & hibernate-release-4.2.2.Final/../ConnectionProviderInitiator.java & 15168494 & 2016-02-24 \\
		16 & hibernate-release-4.2.2.Final/../SchemaUpdate.java & 23520731 & 2016-02-05 \\
		17 & jasperreports-3.7.4/../JRVerifier.java & 8037824 & 2011-05-20 (deleted) \\
		18 & jasperreports-3.7.4/../JRVerifier.java & 8037824 & 2013-12-08 \\
		19 & jasperreports-3.7.4/../SpiderWebPlot.java & 21998949 & 2013-11-22 \\
		20 & jasperreports-3.7.4/../SpiderWebPlot.java & 21998949 & 2013-11-22 \\
		21 & jasperreports-3.7.4/../AbstractXYItemRenderer.java & 12936580 & 2016-01-16 \\
		22 & jfreechart-1.0.13/../KeyToGroupMap.java & 16058183 & 2013-07-03 \\
		23 & jgraph-latest-bsd-src/../GroupingRemoving.java & 6722760 & 2005-xx-xx (rewritten) \\
		24 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & 2005-xx-xx (rewritten) \\
		25 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & 2005-xx-xx (rewritten) \\
		26 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & 2005-xx-xx (rewritten) \\
		27 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & 2005-xx-xx (rewritten) \\
		28 & junit-4/org/junit/Assert.java & 23586872 & 2015-05-12 \\
		29 & junit-4/../ExpectException.java & 8802082 & 2014-05-26 \\
		30 & junit-4/../ExternalResource.java & 7504040 & 2016-06-25 \\
		\hline
	\end{tabular} 
\end{table*}
